---
title: "Chapter 2 - Statistical Learning"
author: "Thalles Quinaglia Liduares"
date: "01/03/2022"
output: html_document
---
# Applied Exercise 2.8

Upload packages

```{r, message=FALSE, warning=FALSE}

library(dplyr)

```


**This exercise relates to the College data set, which can be found in**
**the file College.csv. It contains a number of variables for 777 different**
**universities and colleges in the US.Before reading the data into R,**
**it can be viewed in Excel or a text editor.**

**(a) Use the `read.csv()` function to read the data into R. Call the**
**loaded data college. Make sure that you have the directory set**
**to the correct location for the data.**

```{r}

setwd("C:\\Program Files\\R\\Machine Learning")

data<-read.csv("data.csv")


```

**(b) Look at the data using the fix() function. You should notice**
**that the first column is just the name of each university. We don’t**
**really want R to treat this as data. However, it may be handy to**
**have these names for later. Try the following commands:**

```{r}

data<-data[,-1]

```
**(c) i. Use the summary() function to produce a numerical summary**
**of the variables in the data set.**

```{r}
summary(data)
```

**ii. Use the pairs() function to produce a scatterplot matrix of**
**the first ten columns or variables of the data. Recall that**
**you can reference the first ten columns of a matrix A using A[,1:10].**

```{r}
first_ten_col<-data[,1:10]
pairs(first_ten_col)
```

**iii. Use the plot() function to produce side-by-side boxplots of**
**Outstate versus Private.**

```{r}

#Is giving Error

#data$private<-as.factor(data$private)

#plot(data$private, data$outstate, xlab="Private University", ylab="Tuition in Dollars ($)")

```
**iv. Create a new qualitative variable, called Elite, by binning**
**the Top10perc variable. We are going to divide universities**
**into two groups based on whether or not the proportion**
**of students coming from the top 10 % of their high school**
**classes exceeds 50 %.**

```{r}
Elite<-rep("No",nrow(data))
Elite[data$top10perc >50]<-"Yes"
Elite<-as.factor(Elite)
data<-data.frame(data,Elite)
```

**Use the summary() function to see how many elite universities there are.** 
**Now use the plot() function to produce side-by-side boxplots of Outstate versus Elite.**

```{r}
summary(Elite)

plot(data$Elite, data$outstate, xlab="Elite University", ylab="Tuition in dollars ($)")
```


**v. Use the hist() function to produce some histograms with**
**differing numbers of bins for a few of the quantitative variables.**
**You may find the command par(mfrow=c(2,2)) useful:**
**it will divide the print window into four regions so that four**
**plots can be made simultaneously. Modifying the arguments**
**to this function will divide the screen in other ways.**

```{r}
par(mfrow=c(2,2))

hist(data$apps, xlab="Applications Received", main="")
hist(data$books, xlab="Estimated Cost of Books", main="")
hist(data$phd, xlab="Percentual of Phd's", main="")
hist(data$enroll, xlab=" Number of new students enrolled", main="")
```

**vi. Continue exploring the data, and provide a brief summary**
**of what you discover.**

Lets see how many books cost above the average

```{r}
books_above_avg<- data %>%
        filter(books >=mean(books)) %>%
        summarise(n=n())
books_above_avg
```
Hence, 354 books costs above the average price.


