---
title: "Chapter 2 - Statistical Learning"
author: "Thalles Quinaglia Liduares"
date: "01/03/2022"
output: html_document
---

# Applied Exercise 2.9

Upload packages

```{r, warning=FALSE, message=FALSE}

library(dplyr)
library(tibble)

```

Upload database

```{r, warning=FALSE, message=FALSE}
setwd("C:\\Program Files\\R\\Machine Learning")

data<-read.csv("auto-mpg.csv")

data1<-tibble::as_tibble(data) # Transforming the dataframe in tibble to facilitate the analysis.
```



**This exercise involves the Auto data set studied in the lab. Make sure**
**that the missing values have been removed from the data.**

**(a) Which of the predictors are quantitative, and which are qualitative?**

```{r}
glimpse(data1)
```

The dataframe contains 9 variables.  

7 variables are quantitative and 2 are qualitative.

**(b) What is the range of each quantitative predictor? You can answer this using the range() function**

```{r}
num_var<- select_if(data1, is.numeric) 

num_var # Note that only numerical variables were selectioned.

for (var in num_var) {
  
  print(range(var))
  
}

```
**(c) What is the mean and standard deviation of each quantitative predictor?**

The mean values are equal to 

```{r}
for (var in num_var) {
  print(round(mean(var),2))

  
}
```
And the `sd` for quantitative variables are equal to

```{r}
for (var in num_var) {
  print(round(sd(var),2))
}
```
**(d)Now remove the 10th through 85th observations. What is the range, mean, and standard deviation of each predictor**
**in the subset of the data that remains?**

```{r}
# In progress..
```

**(e) Using the full data set, investigate the predictors graphically,**
**using scatterplots or other tools of your choice. Create some plots**
**highlighting the relationships among the predictors. Comment**
**on your findings.**



```{r}
pairs(num_var)

par(mfrow=c(2,2)) 

plot(data1$mpg,data1$cylinders, xlab="mpg", ylab="cylinders", main="")

hist(data1$cylinders, xlab="cylinders", main="")

barplot(data1$cylinders, xlab="cylinders", main="")

boxplot(data1$cylinders~data1$acceleration, xlab="cylinders",ylab="acceleration", main="")




```


**(f) Suppose that we wish to predict gas mileage (mpg) on the basis**
**of the other variables. Do your plots suggest that any of the**
**other variables might be useful in predicting mpg? Justify your**
**answer.**

```{r}
# In progress..
```



