---
title: "Chapter 3 - Linear Regression"
author: "Thalles Quinaglia Liduares"
date: "04/03/2022"
output: html_document
---

# Applied Exercise 3.9

Upload packages 

```{r, warning=FALSE, message=FALSE}

library(dplyr)
library(lmreg)
library(readxl)
library(corrplot)

source("http://www.sthda.com/upload/rquery_cormat.r")
```

Upload Database

```{r, warning=FALSE, message=FALSE}
setwd("C:\\Program Files\\R\\Machine Learning")

data<-readxl::read_excel("C:\\Program Files\\R\\Machine Learning\\auto-mpg.xlsx")

```

**9. This question involves the use of multiple linear regression on the**
**Auto data set.**

**(a) Produce a scatterplot matrix which includes all of the variables**
**in the data set.**

```{r}

var_num <- select_if(data, is.numeric)   

pairs(var_num)
          
```
**(b) Compute the matrix of correlations between the variables using**
**the function cor(). You will need to exclude the name variable, cor() which is qualitative**


```{r}

rquery.cormat(var_num)

```
**(c) Use the `lm()` function to perform a multiple linear regression**
**with `mpg` as the response and all other variables except `name` as**
**the predictors. Use the `summary()` function to print the results.**
**Comment on the output.**

```{r}

options(scipen=999)

lm1<-lm(mpg~cylinders+displacement+horsepower+weight+acceleration+factor(origin)+factor(`model year`), data)

summary(lm1)
```

Among the characteristics of the car, only the variable `weight` has significance to the 1% level. The 
variable `displacement` shows statistical significance to the 5% level. The Adjusted R-Squared is 0.847. 
So, 84.7% of the variability in `mpg` is explaneid by the predictors. The cathegorical variable `year` suggests 
that cars perform more `mpg`, due mostly to the technological innovations.

**(d) Use the plot() function to produce diagnostic plots of the linear**
**regression fit. Comment on any problems you see with the fit.**
**Do the residual plots suggest any unusually large outliers? Does**
**the leverage plot identify any observations with unusually high**
**leverage?**

```{r}

par(mfrow=c(2,2))
plot(lm1)
```

The `Normal -QQ` plot shows that residuals follow a normal distribution, because the points 
fits well the dashed straight line. The `Residuals vs Fitted` plot shows the horizontal red straight line
that's a good indication that model follows a linear pattern.
