---
title: "Chapter 3 - Linear Regression"
author: "Thalles Quinaglia Liduares"
date: "02/03/2022"
output: html_document
---

# Applied Exercise 3.8

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(tibble)
library(dplyr)
library(readxl)
```
Upload database

```{r}

setwd("C:\\Program Files\\R\\Machine Learning")

data<-readxl::read_excel("auto-mpg.xlsx")

str(data)


```
**8. This question involves the use of simple linear regression on the Auto data set.**

**(a) Use the `lm()` function to perform a simple linear regression with**
**mpg as the response and horsepower as the predictor. Use the**
**`summary()` function to print the results.**

```{r}

lm1<-lm(data$mpg~data$horsepower)

summary(lm1)
```
The estimated equation is given by $$\widehat{mpg}=39.9-0.15mpg$$
Hence, there's a negative relationship between these two variables. Both the intercept
and slope coefficient are statistically significant at the p-value <0.001.

For each additional `hp` in the car, the `mpg` diminishes 0.15

If `hp`=98, then $mpg=39.9-0.15(98)=25.2$

The confidence interval is equal to

```{r}
confint(lm1)
```
**(b) Plot the response and the predictor. Use the abline() function**
**to display the least squares regression line.**

```{r}


plot(data$mpg, data$horsepower)



# The abline function is giving error

#abline(lm1)
```


**(c) Use the `plot()` function to produce diagnostic plots of the least**
**squares regression fit. Comment on any problems you see with the fit.**
```{r}

par(mfrow=c(2,2))

plot(lm1)


```

Based on `Residual vs Fitted` plot, might exist a linear relationship between the `mpg` and `hp`, cause the points are well distributed along the red line.

The `Normal Q-Q` plot confirms the normal distribution of residuals, cause the points are well adjusted to the straigth line.

The `Residuals vs Leverage` analyses the influence of outliers. Besides the possible influence of observations 117 and 84, as showed in the plot, the distribution is well-behaved, as measured by the Cook Distance.

