---
title: "Chapter 3 - Linear Regression"
author: "Thalles Quinaglia Liduares"
date: "04/03/2022"
output: html_document
---

# Applied Exercise 3.11

Upload packages

```{r, warning=FALSE, message=FALSE}
library(lmreg)
```
Generate the sample model

```{r}
set.seed(1)
x=rnorm(100)
y=2*x+rnorm (100)
```



**(a) Perform a simple linear regression of `y` onto `x`, without an intercept. Report the coefficient estimate**
**$\hat{\beta}$, the standard error of this coefficient estimate, and the t-statistic and p-value associated with the null**
**hypothesis $H_0: \beta=0$. Comment on these results**

```{r}

lm1<-lm(y~x-1)
summary(lm1)
```

The estimated model is expressed as follows

$$\hat{y}=1.993x$$

The standard error, t-statistic and p-value are 0.106, 18.73 and 2e-16, respectively.

```{r}


```



**In this problem we will investigate the t-statistic for the null hypothesis $H_0: \beta=0$**
**in simple linear regression without an intercept. To begin, we generate a predictor**
**`x` and a response `y` as follows.**


```{r}
set.seed(1)
x=rnorm(100)
y=2*x+rnorm (100)
 
```

**(b) Now perform a simple linear regression of x onto y without an**
**intercept, and report the coefficient estimate, its standard error,**
**and the corresponding t-statistic and p-values associated with**
**the null hypothesis $H_0: \beta=0$.**

```{r}
lm2<-lm(x~y-1)

summary(lm2)
```

The estimated model is expressed as follows

$$\hat{x}=0.39y$$

The standard error, t-statistic and p-value are 0.02, 18.73 and 2e-16, respectively.

**(c) What is the relationship between the results obtained in (a) and (b)?**

The principal difference between these models, is the magnitude of slope in curve.
In the item (a), the slope is 2, as in item (b) is 0.4, aproximately.

