---
title: "Chapter 3 - Linear Regression"
author: "Thalles Quinaglia Liduares"
date: "04/03/2022"
output: html_document
---

# Applied Exercise 3.10

Upload packages

```{r, message=FALSE, warning=FALSE}
library(lmreg)
library(ISLR)

```
upload database

```{r, warning=FALSE, message=FALSE}
data<-ISLR::Carseats
```


**10. This question should be answered using the Carseats data set**

**(a) Fit a multiple regression model to predict `Sales` using `Price`,**
**`Urban`, and `US`.**

```{r}
lm1<-lm(Sales~Price+factor(Urban)+factor(US), data)

summary(lm1)
```

**(b) Provide an interpretation of each coefficient in the model. Be**
**careful—some of the variables in the model are qualitative!**

The estimated equation is given by $$\widehat{Sales}=13.04-0.05Price-0.02Urban+1.20US \\  (1)$$

If the price of carseat, represented by the variable `Price`, increases $1, the mountant of Sales decreases
\$0.05, _ceteris paribus_.Controlling for store in US, the mountant of sales is $1.20 higher in relation
one store out of US.

**(c) Write out the model in equation form, being careful to handle**
**the qualitative variables properly**

Given by (1).

**(d) For which of the predictors can you reject the null hypothesis**
$H_0: \beta_j=0$?

The following variables have statistical significance to the 1% level: `Intercept`, `Price` and `US`.

The variable `Urban` do not have statistical significance.

**(e) On the basis of your response to the previous question, fit a**
**smaller model that only uses the predictors for which there is**
**evidence of association with the outcome.**

```{r}
lm2<-lm(Sales~Price+US, data)

summary(lm2)
```
In this case, there's only one slightily difference between the estimated coefficients.

**(f) How well do the models in (a) and (e) fit the data?**

In both cases, with base on R-Squared, the models is aproximatelly 23% explaneid 
by the predictor variables.

**(g) Using the model from (e), obtain 95 % confidence intervals for**
**the coefficient(s).**

```{r}
confint(lm2)
```

**(h) Is there evidence of outliers or high leverage observations in the**
**model from (e)?**

```{r}

par(mfrow=c(2,2))

plot(lm2)
```

As showed by the `Residuals vs Leverage` plot, the observations #26 and #368
might be outliers, as measured by Cook distance.
